\documentclass{resume}
\usepackage[hidelinks]{hyperref}
\usepackage{lipsum}
\usepackage{standalone}

\name{Joshua Petitma}
\contact{\href{mailto:joshua.petitma@duke.edu}{joshua.petitma@duke.edu}}
\contact{\href{https://github.com/joshpetit}{https://github.com/joshpetit}}
\contact{\href{https://linkedin.com/in/joshua-petitma}{https://linkedin.com/in/joshua-petitma}}
\contact{Durham, North Carolina}
\contact{\href{tel:757-632-9220}{757-632-9220}}

\begin{document}
%\include{cover_letter.tex}
\pagebreak
\makeheader

\newcommand{\skill}[2]{\textbf{#1} - #2}


\begin{ResumeSection}{experience}
    \begin{ResumeSubsection}{org={Sam Entertainment AG},location={Zurich,
        Switzerland (remote)},position={Part-time Software Engineer (Mobile)},duration={January
    2023 - Present}}
        \begin{itemize}
            \item Lead developer responsible for implementing core features for the Sam app with over 500,000
                downloads.
            \item Improved app startup speed by 50\% by rearchitecting
                authentication and caching data from previous launches.
            \item Improved upload consistency and speed by
                fifteen times through HTTP multipart requests and taking time to refactor
                uploading UI \& logic to be easier to follow.
        \end{itemize}
    \end{ResumeSubsection}

    \begin{ResumeSubsection}{org={Amazon},location={San Francisco,
        California},position={Software Engineering Intern (iOS)},duration={May 2023 -
    July 2023}}
        \begin{itemize}
            \item Used SwiftUI and UIKit to create and integrate screens into
                the Amazon Music app for iOS.
            \item Collaborated with senior developers to help migrate legacy
                callback code to the async/await.
        \end{itemize}
    \end{ResumeSubsection}
    \begin{ResumeSubsection}{org={Amazon},location={San Francisco,
        California},position={Software Engineering Intern (Web)},duration={May
    2022 - August 2022}}
        \begin{itemize}
            \item Created a tool to allow
                non-technical stakeholders to interface with Amazon Music's automation
                system.
            \item Developed tool as a web app with ReactJS and TypeScript and integrated
                into Amazon's pipelines.
        \end{itemize}
    \end{ResumeSubsection}

    \begin{ResumeSubsection}{org={Life.Church YouVersion},location={Edmond,
        Oklahoma},position={Software Engineering Intern (Web)},duration={May 2021 - August 2021}}
        \begin{itemize}
            \item {Created a real-time web feature allowing hundreds of thousands of
                users to like messages during livestreams.}
            \item {Used React, Typescript, CSS animations, and PubNub APIs to
                show real-time reactions.}
            \item Gained important leadership and personal development skills
                through weekly development meetings.
        \end{itemize}
    \end{ResumeSubsection}

    \begin{ResumeSubsection}{
            org={Private Consulting Company},
            location={Virginia Beach, Virginia (remote)},
            position={Lead Fullstack Engineer},
            duration={June 2021 - December 2022}
        }
        \begin{itemize}
            \item {Led a four-person team to develop an app for a Virginia consulting company.}
            \item {Implemented client app in Flutter and used Firebase for the backend.}
            \item {Created GitHub CI/CD for automatic backend deployment as well as code quality and test validation.}
        \end{itemize}
    \end{ResumeSubsection}


    % \begin{ResumeSubsection}{org={Petit Development, LLC},position={Founder},duration={August 2021 - Present},location={Virginia}}
    %     \begin{itemize}
    %         \item Founded LLC for freelance mobile and web apps for small businesses.
    %     \end{itemize}
    % \end{ResumeSubsection}

\end{ResumeSection}


\begin{ResumeSection}{projects}
    \begin{ResumeProject}{org={Bible Ram, Flutter
        App},location={\href{https://bibleram.app}{https://bibleram.app}}}
        \begin{itemize}
            \item {Developed an opensource multiplatform app with Flutter to
                help memorize Bible passages.} 
            \item {Used NOSQL database for serializing app data and SQLite for
                storing translations.}
        \end{itemize}
    \end{ResumeProject}
    \begin{ResumeProject}{org={Widgetbook},location={\href{https://www.widgetbook.io/}{https://widgetbook.io}},position={Core Contributor},duration={January 2022 - April 2022}}
        \begin{itemize}
            \item Collaborated with core maintainers to develop the ``knobs"
                feature for open-source Flutter Storybook.js clone.
        \end{itemize}
    \end{ResumeProject}
    \begin{ResumeProject}{org={Send, Full Stack Web App},location={\href{https://send.petit.dev}{https://send.petit.dev}}}
        \begin{itemize}
            \item {Designed and created a responsive \href{https://send.petit.dev}{website} to store and retrieve links identified by short text.}
            \item {Implemented frontend with TypeScript, Next.js, and
                TailwindCSS while using Firebase Firestore for storage.}
            \item {Created Next.js API to allow users to retrieve
                information via a REST API.}
        \end{itemize}
    \end{ResumeProject}
\end{ResumeSection}

\begin{ResumeSection}{education}
    \begin{ResumeSubsection}{org={Duke University},position={Bachelor of Science in Computer Science}
        ,duration={August 2020 - May 2024}, location={GPA: 3.65}}
        \begin{itemize}
            \item \skill{Coursework}{
                    Advanced Software Design/Implementation, 
                    %Web Project Design,
                     Data Structures and Algorithms
            }
            \item \skill{Clubs}{Started and led an Adventist Christian
                Fellowship at Duke.}
            \item \skill{Notable Achievements}{Recipient of the Gates
                    Scholarship and Hadden Scholarship}
        \end{itemize}
    \end{ResumeSubsection}
\end{ResumeSection}

\begin{ResumeSection}{Languages and Technologies}
        \begin{itemize}
            \item \skill{Programming Languages}{TypeScript, JavaScript,
                Python, Java, Dart, HTML}
            \item \skill{Technologies}{Flutter, Next.js, React, Tailwind CSS, Selenium, 
                Firebase, Linux, REST APIs}
            %\item \skill{Soft Skills}{Leadership, Communication, Team Builder, Intentionality}
        \end{itemize}
\end{ResumeSection}

\end{document}
