\documentclass{resume}
\usepackage[hidelinks]{hyperref}
\usepackage{lipsum}

\name{Joshua Petitma}
\contact{\href{tel:757-632-9220}{757-632-9220}}
\contact{\href{mailto:joshua@petit.dev}{joshua@petit.dev}}
\contact{\href{https://github.com/joshpetit}{https://github.com/joshpetit}}
\contact{\href{https://linkedin.com/in/joshua-petitma}{https://linkedin.com/in/joshua-petitma}}

\begin{document}
\makeheader

\newcommand{\skill}[2]{\textbf{#1} - #2}

\begin{ResumeSection}{education}
    \begin{ResumeSubsection}{location={GPA: 3.9},org={Duke University},position={Bachelor of Science in Computer Science}
        ,duration={August 2020 - May 2024}}
        \begin{itemize}
            \item \skill{Relevant Coursework}{Advanced Software Design/Implementation, Web Project Design, Computer Architecture,
                Data Structures and Algorithms, Discrete Math for Computer Science}
            \item \skill{Clubs}{Started and leads an Adventist Christian Fellowship between Duke and UNC.}
            \item \skill{Notable Achievements}{Gates Scholar, Meredith Mallory
                George Scholar, Youth-Foundation scholar}
        \end{itemize}
    \end{ResumeSubsection}
\end{ResumeSection}

\begin{ResumeSection}{experience}
    \begin{ResumeSubsection}{org={Life.Church YouVersion},location={Edmond, Oklahoma},position={Software Engineering Intern},duration={May 2021 - August 2021}}
        \begin{itemize}
            \item {Created the ability to like chat messages within
                    the Church Online Platform, a livestreaming service used by
                thousands of churches globally.}
            \item {Used React, Typescript, CSS animations, and
                PubNub APIs to implement real time reactions.}
            \item Gained important leadership and personal development skills
                through weekly development meetings.
        \end{itemize}
    \end{ResumeSubsection}

    \begin{ResumeSubsection}{org={Widgetbook},location={Germany (remote)},position={Winter Software Engineering Intern},duration={January 2022 - April 2022}}
        \begin{itemize}
            \item Incoming winter intern at Widgetbook, an opensource backed startup based in Germany.
            \item Will work on developing features for their flutter package which allows users to view Flutter widgets in the browser.
        \end{itemize}
    \end{ResumeSubsection}

    \begin{ResumeSubsection}{org={Virginia Consulting Company},location={Virginia Beach, Virginia},position={Lead App Developer},duration={June 2021 - December 2021}}
        \begin{itemize}
            \item {Technical Lead of a four person team developing an app for a Virginia consulting company.}
            \item {Implementing client app in Flutter and using Firebase's platform as a service for a backend.}
            \item {Created GitHub CI/CD pipeline for automatic backend deployment as well as code quality and test validation.}
        \end{itemize}
    \end{ResumeSubsection}


    \begin{ResumeSubsection}{org={Petit Development, LLC},position={Founder},duration={August 2021 - Present},location={Virginia}}
        \begin{itemize}
            \item Founded LLC for creating open source applications as well as
                websites for small businesses.
            \item Works with non-profits to create professional website at no cost.
        \end{itemize}
    \end{ResumeSubsection}

    \begin{ResumeSubsection}{org={Duke University CS Department},location={Durham, North Carolina},position={Advanced Software Design Teaching Assistant},duration={August 2021 - Present}}
        \begin{itemize}
            \item Helps design course for students and make decisions on teaching topics and order.
            \item Develops videos to help students learn technical skills in Java and JavaFX.
            \item Mentors students in weekly meetings to help track progress and grow intentionally as software engineers.
        \end{itemize}

    \end{ResumeSubsection}
\end{ResumeSection}


\begin{ResumeSection}{projects}
    \begin{ResumeSubsection}{org={RefBible},location={\href{https://github.com/joshpetit/refbible}{joshpetit/refbible}}}
        \begin{itemize}
            \item {Developed Bible app in Flutter that allows users to save
                favorite verses and search verses by topic and context.} 
            \item {Persisted user preferences and favorites in local storage and
                created APIs to retrieve bible texts.}
        \end{itemize}
    \end{ResumeSubsection}
    \begin{ResumeSubsection}{org={Send},location={\href{https://send.petit.dev}{https://send.petit.dev}}}
        \begin{itemize}
            \item {Created responsive \href{https://send.petit.dev}{website} to store and retrieve links identified by short text.}
            \item {Implemented frontend with TypeScript, Next.js, TailwindCSS, and deployed to Vercel. Used Firebase Cloud Firestore for data storage.}
            \item {Created Next.js API to allow users to retrieve information from the command line with cURL.}
            \item {Designed in
                    \href{https://www.figma.com/file/Rn2hStoJfozlgsvSoEeGnj/Send?node-id=139%3A2}{Figma}
                    to practice creating enjoyable user
                interfaces and responsive design.}
        \end{itemize}
    \end{ResumeSubsection}
    % \begin{ResumeSubsection}{org={Colors},location={\href{https://colors.petit.dev}{https://colors.petit.dev}}}
    %     \begin{itemize}
    %         \item {Designed \href{https://colors.petit.dev}{website}
    %             in Figma as a case study to practice creating enjoyable user interfaces and experiences.} 
    %         \item {Implemented website with TypeScript, SASS, Next.js, and deployed to Vercel.}
    %         \item {Created Next.js API to generate files of custom size, color, and filetype to experiment with API route design.}
    %     \end{itemize}
    % \end{ResumeSubsection}
    % \begin{ResumeSubsection}{org={Collegiate Covid},position={2020 DukeHacks Hackathon},location={\href{https://collegiatecovid.com}{https://collegiatecovid.com}}}
    %     \begin{itemize}
    %         \item {Led team of four to build analytics website for covid metrics across U.S universities.}
    %         \item Built backend in python to scrape statistics from college dashboards and post them to firebase.
    %         \item Used Javascript and React to display data from Firebase, deployed frontend to Firebase hosting.
    %     \end{itemize}
    % \end{ResumeSubsection}
\end{ResumeSection}

\begin{ResumeSection}{skills}
    \begin{ResumeSubsection}{}
        \begin{itemize}
            \item \skill{Languages}{Dart, TypeScript, Java, Python}
            \item \skill{Software}{Flutter, React, Firebase, Next.js, Tailwind CSS}
        \end{itemize}
    \end{ResumeSubsection}
\end{ResumeSection}

\end{document}
